\documentclass[a4paper,10pt]{article}
\usepackage{polski}
\usepackage[utf8]{inputenc}
\usepackage{array}
%custom margins
\usepackage[left=2.5cm, top=2.5cm, bottom=3cm, right=2cm, foot=2cm, head=0.5cm]{geometry}
\usepackage{fancyhdr}
\usepackage[bookmarks=true, pdftex]{hyperref}

%styl nagłówków
\pagestyle{fancy}
\parindent 2cm

%opening
\title{Notatka specjalna}
\author{3@KASK}

\begin{document}
\bibliographystyle{plain}


\maketitle


\begin{center}
%budowanie tabeli
\begin{tabular}{|p{7cm}|p{7cm}|}
\hline
Symbol projektu: & Opiekun projektu:   \tabularnewline
3@KASK & mgr inż. Tomasz Boiński    \tabularnewline \hline
\multicolumn{2}{|l|}{Nazwa Projektu: } \tabularnewline
\multicolumn{2}{|l|}{Wizualizacja grafów za pomocą biblioteki Prefuse } \tabularnewline
\hline
\multicolumn{2}{l}{ } \tabularnewline %pusta linijka
\hline
Nazwa Dokumentu: & Data sporządzenia:   \tabularnewline
Notatka specjalna & 16 czerwca 2009 \tabularnewline \hline
Odpowiedzialny za dokument: & Przeznaczenie:   \tabularnewline
Anna Jaworska & INFORMACYJNE \tabularnewline \hline
\end{tabular}
\end{center}



\section{Wyjaśnienie}
Postanowiliśmy wzorować się w zakresie wyglądu na programie do wizualizacji ontologii  GrOWL\footnote{\url{http://www.uvm.edu/~skrivov/growl/}}, stworzonym na Uniwersytecie w Vermont. Jako, że został on stworzony w języku JAVA z wykorzystaniem biblioteki Prefuse możliwe będzie, że skorzystamy także z części kodu jako wzorca. Dlatego potrzebowaliśmy potwierdzenia twórcy tego programu - pana Sergeya Krivova odnośnie licencji dla tego programu. Uzyskana odpowiedź załączona jest poniżej.


\section{Treść emaila}

\begin{quote}

From: valanthe86@gmail.com [mailto:valanthe86@gmail.com] On Behalf Of Anna Jaworska
Sent: Saturday, May 16, 2009 9:43 AM
To: skrivov@uvm.edu
Subject: GrOWL - question about licence


Dear Mr. Sergey Krivov,

Department of Computer <http://www.eti.pg.gda.pl/katedry/kask/>  Architecture of
Faculty of Electronics, Telecommunications and Informatics at Gdansk University of
Technology in Poland is currently developing its own system for creating and storing
ontologies.

A module of this system is going to be an application which will provide
visualization of ontologies. I am a part team of students who were assigned to
create Java library which incorporates both ontology processing and presenting it in
form of graph needed to build this module.

I have stumbled upon GrOWL, and I must admit it is one of the best application for
ontology visualization I have seen during our research. Our team would like to take
similar approach in ontology visualization, since we also plan on using Prefuse
graphics library.

That gets me to my question. You mention in your publications that GrOWL is "open
source", however neither code nor your papers mention any specific licence like GNU
GPL. This issue is important for our deparment because it has various legal
consequences.

Can you provide me with an official stament regarding GrOWL licencing? I would
really appreciate your prompt response.

Sincerely,

Anna Jaworska

Student at ETI Faculty at Gdansk University of Technology



\end{quote}
\newpage
\begin{quote}
 Subject:   	RE: GrOWL - question about licence
From:   	"Sergey Krivov" <Serguei.Krivov@uvm.edu>
Date:   	Sat, May 16, 2009 16:00
To:   	"'Anna Jaworska'" <Anna.Jaworska@zak.eti.pg.gda.pl>
Cc:   	"'Ferdinando Villa'" <fvilla@uvm.edu>

Dear Anna,

Thanks for your letter, it is always pleasant to hear that GrOWL is “..one of the
best application for ontology visualization….”



Official statement from me about GrOWL license:



GrOWL has been released under GNU GPL license   which is available at
http://www.gnu.org/copyleft/gpl.html



In case you have  questions about other possible licensing options please contact
Ferdinando Villa, whom I CC this email.



Good luck with developing your own system,  I will appreciate if you notify me when
you make the first release.



Best Regards,

Sergey

**********************

Sergey Krivov,

Research Assistant Professor,

Computer Science Dept.,

University of Vermont,

617 Main,

Burlington, VT, 05405.



\end{quote}


\end{document}
